---
title: "Week5"
author: "Brandon"
date: "June 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
```

import yob2016.txt into R. Make sure it contains three columns with hum-readable column names.

```{r}

setwd("C:/Users/brndn/OneDrive/Documents")
df <- read.table("yob2016.txt", header = FALSE)
df <-str_split_fixed(df[,1], ";",3)
colnames(df) <- c("Names", "Gender", "Other_Children")
head(df)
summary(df)

```


Display the summary and structure of df

```{r}
dim(df)
summary(df)
head(df,20)
```

Where is the name which was misspelled with three "yyy's" at the end of the name?

```{r}
grep("yyy$", df, value=TRUE)
```



Upon finding the misspelled name, please remove this particular observation, as the client says it’s redundant.  Save the remaining dataset as an object: y2016 

```{r}
grep("{2}yyy$", df, value=FALSE)
y2016<-df[-(212),]
```

a.	Like 1a, please import the yob2015.txt file into R.  Assign the dataframe to y2015.

```{r}
library(stringr)
setwd("C:/Users/brndn/OneDrive/Documents")
y2015<-read.table("yob2015.txt",header=FALSE)
y2015 <-str_split_fixed(y2015[,1], ",",3)
colnames(y2015) <- c("Names", "Gender", "Other_Children")
tail(y2015,10)
```

Display the last ten rows in the dataframe.  Describe something you find interesting about these 10 rows.

```{r}
tail(y2015,10)
```
The last 10 rows of the data.frame "y2015" contain all names beginning with the letter "Z".  This alone isn't interesting (except that people named their child "Zolton").  What is interesting, from a naming perspective, is that there doesn't seem to be any female names in the last 10 rows, and the instances of naming (by number of children) is all 5 observations.

Merge y2016 and y2015 by your Name column; assign it to final.  

```{r}
final <- merge(y2015,y2016, by=c("Names","Gender","Other_Children"), all=TRUE)
library(plyr)
library(data.table)
final[,3] <-as.numeric(as.character(final[,3]))
final2<-data.table(final)
final3<-final2[,lapply(.SD,sum), by = list(Names,Gender)]
```

In previous step, combined the "Other_children" column together given the "Names" and "Gender" variables.  This means, that the "total" column, for that particular data.table is now already the equivalent of the "Total" column.  So this column will be renamed "Total" for the "final3" data.  

```{r}
colnames(final3)[3] <- "Total"
dim(final3)
```

Sort the data by Total.  What are the top 10 most popular names?

```{r}
final4<-final3[order(-Total),]
head(final4,10)
```

Omit boys and give the top 10 most popular girl’s names.
```{r}
final5 <- final4[Gender != "M"]
head(final5,10)
```

Write these top 10 girl names and their Totals to a CSV file.  Leave out the other columns entirely.

```{r}
final6 <- final5[,-(2:3)]
final7<- head(final6,10)
write.csv(final7, file = "FinalHomework5.csv")
```






