---
title: "Homework4"
author: "Brandon"
date: "June 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1a.  Installed FiveThirtyEight data.

```{r}
install.packages("fivethirtyeight", repos = 'http://cran.us.r-project.org')
library(fivethirtyeight)
```

##1b.  Assigned the 18th dataset (or college_all_ages) as the object "df"

```{r}
df <- college_all_ages
```

## 1c. This dataset "college_all_ages" was analyzed as part of the story 'The Economic Guide to Picking a College Major'.https://fivethirtyeight.com/features/The-Economic-Guide-to-Picking-a-College/

##1d. with the R command "dim()", give the dimensions and column names "colnames()"

```{r}
dim(df)
colnames(df)
```
              
#2a. Column names and then counts the number of columns but not rows.

```{r}
colnames(df)
ncol(df)
```

#2b.Generate a count of each unique major_category and assign it to major_count.

```{r}
library(plyr)
major_count <- count(df, vars=c("major_category"))
print(major_count)
```

#2c.	par(las=2) before the plot; barplot of major_count; label the title with something informative; label x and y axis; change color; assign major_category lables to their respective bar; flip the barplot horizontal  use barplot()

```{r}
barplot(major_count$freq, names.arg=major_count$major_category,las=2,main = "College Students by Major Category",xlab = "Major Category",ylab = "Frequency",col = "darkred", horiz = TRUE,ylim = c(0,30))
```






##2d.	Fivethirtyeight data to CSV (df file)

```{r}

write.csv(college_all_ages, file = "Fivethirtyeight.csv")
```



GITHUB REPO

https://github.com/bdelahoussaye/6306_Homework_Files

