---
title: "Homework3"
author: "Brandon"
date: "May 21, 2018"
output: html_document
---

#Questions 1:  GitHub Cloning (20 points): Using Git, clone the following GitHub repository to your local machine: https://github.com/caesar0301/awesome-public-datasets.  In RMarkdown, please show the ccaode (commented out, as it's not R syntax) that you used to create a new directory, navigate to the appropriate directory, and clone the repository to it.  Like actual Git, one command per line/, please.



brndn@LAPTOP-TFJDQUU9 MINGW64 ~
$ ls
'3D Objects'/
 Anaconda3/
 Analysis/
 AppData/
'Application Data'@
 Contacts/
 Cookies@
 Desktop/
 Documents/
 Downloads/
 Favorites/
'hello world from file.ipynb'
'Hello World.ipynb'
 IntelGraphicsProfiles/
 Links/
'Local Settings'@
 MicrosoftEdgeBackups/
 Music/
'My Documents'@
 NetHood@
 NTUSER.DAT
 ntuser.dat.LOG1
 ntuser.dat.LOG2
 NTUSER.DAT{d982a088-40fd-11e8-8245-fc4596e91393}.TM.blf
 NTUSER.DAT{d982a088-40fd-11e8-8245-fc4596e91393}.TMContainer00000000000000000001.regtrans-ms
 NTUSER.DAT{d982a088-40fd-11e8-8245-fc4596e91393}.TMContainer00000000000000000002.regtrans-ms
 ntuser.ini
 OneDrive/
 PicStream/
 Pictures/
 PrintHood@
 Recent@
 Roaming/
'Saved Games'/
 Searches/
 SendTo@
'Start Menu'@
 Templates@
 Untitled.ipynb
 Untitled1.ipynb
 Untitled2.ipynb
 Untitled3.ipynb
 Untitled4.ipynb
 Untitled5.ipynb
 Videos/
'VirtualBox VMs'/

brndn@LAPTOP-TFJDQUU9 MINGW64 ~
$ cd OneDrive

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive
$ ls
 desktop.ini          'Getting started with OneDrive.pdf'
 Documents/            Pictures/
'Email attachments'/  'PwC_Intercompany_Assessment_for_061217 v18c.pptx'

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive
$ cd Documents

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents
$ ls
 42D81330                   'Height (4).csv'        R/
'bridge to stat'/            Hello_txt.txt          SASUniversityEdition/
'computer receipt.jpg'      'Intro Python and R'/  'Semester 1 Courses'/
'Custom Office Templates'/  'My Kindle Content'/    testdir/
 desktop.ini                'My SAS Files'/        'uranium (1).csv'
 ggplot2/                   'Programming Files'/
 GitHub/                    'Python Scripts'/

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents
$ cd Github

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github (master)
$ ls
6306Homework3/  Homework3/  PythonIntroBridge/

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github (master)
$ cd Homework3

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ ls

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ github https://github.com/caesar0301/awesome-public-datasets.git


brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ cd awesome-public-datasets
bash: cd: awesome-public-datasets: No such file or directory

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ ^C

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ git clone https://github.com/caesar0301/awesome-public-datasets.git
Cloning into 'awesome-public-datasets'...
remote: Counting objects: 1475, done.
remote: Compressing objects: 100% (18/18), done.
remote: Total 1475 (delta 26), reused 40 (delta 24), pack-reused 1433
Receiving objects: 100% (1475/1475), 544.54 KiB | 641.00 KiB/s, done.
Resolving deltas: 100% (859/859), done.

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ ls
__MACOSX/  awesome-public-datasets/  titanic.csv

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3 (master)
$ cd awesome-public-datasets/

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3/awesome-public-datasets (master)
$ ls
Datasets/  LICENSE  README.rst

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3/awesome-public-datasets (master)
$ cd Datasets

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3/awesome-public-datasets/Datasets (master)
$ ls
titanic.csv.zip

brndn@LAPTOP-TFJDQUU9 MINGW64 ~/OneDrive/Documents/Github/Homework3/awesome-public-datasets/Datasets (master)
$



# 2.	Data Summary (20 points): From this aforementioned cloned repo, please extract titanic.csv.zip.  To be clear, this does not have to be done in Git or command line.  

##a.	In R, please read in titanic.csv via either read.table() or read.csv(), assigning it to df.  This dataset follows the passengers aboard the Titanic, including their fees paid, rooms rented, and survivorship status.

##b.	Output the respective count of females and males aboard the Titanic. Plot the frequency of females and males.  Be sure to give an accurate title and label the axes.

##c.	Please use one apply function (to review: swirl() modules 11, 12) to output the means of Age, Fare, and Survival.  Make sure the output is a real number for all three means.


```{r}
getwd()
setwd("C:/Users/brndn/OneDrive/Documents/GitHub/Homework3")
titanic <- read.csv(file = "titanic.csv", header = TRUE, sep = ",")
table(titanic$Sex)
barplot(table(titanic$Sex), ylim=c(0,800),main = "Titanic Gender Distribution", ylab = "Number of People", xlab = "Sex")
apply(titanic[,c("Survived", "Age", "Fare")],2, mean, na.rm=TRUE)
```

#3.	Function Building (30 points): You research sleep and just got your first data set.  Later, you'll have another dataset with the same column names, so you want to create a helper function that you can analyze this dataset and the next.  Load sleep_data_01.csv (found at http://talklab.psy.gla.ac.uk/L1_labs/lab_1/homework/index.html).  Questions 3A through 3D should be answered in function(x){}.  3E can be outside of the function. 

```{r}
getwd()
setwd("C:/Users/brndn/OneDrive/Documents/GitHub/Homework3")
sleep <- read.csv(file = "sleep_data_01.csv", header = TRUE, sep = ",")
```

##a.	Create objects for the median Age, the minimum and maximum Duration of sleep, and the mean and standard deviation of the Rosenberg Self Esteem scale (RSES).  You may need to specify a few options like in Problem 2 and live session.
##b.	Create a data.frame object called report: it should consist of the median age, the RSES mean and standard deviation respectively divided by five (since there are five questions and these scores are summed), and the range of Duration (the statistical definition of range; it should be a single number.)
##c.	Change the column names of this data.frame to MedianAge, SelfEsteem, SE_SD, and DurationRange.
##d.	Round the report to at most 2 digits: leave this as the closing line to the function.
##e.	Finally, run the function on your sleep data to show the output.

```{r}
myfunction <- function(x) {
  
  MedianAge = median(x$Age,na.rm=TRUE)
  DurationMax = max(x$Duration, na.rm=TRUE)
  DurationMin = min(x$Duration, na.rm=TRUE)
  DurationRange = DurationMax - DurationMin
  RSESMean = mean(x$RSES, na.rm=TRUE)
  RSESStdev = sd(x$RSES, na.rm = TRUE)
  Report <- data.frame(MedianAge/5,RSESMean/5,RSESStdev/5,DurationRange)
  names(Report)[1] <- paste("MedianAge")
  names(Report)[2] <- paste("SelfEsteem")
  names(Report)[3] <- paste("SE_SD")
  names(Report)[4] <- paste("DurationRange")
  Report = round(Report,2)
  return(Report)
  
}
myfunction(sleep)

```


